### 2020-03-23 e3_metg_compute.tex
Tweak spacing around figure captions.
Update text and fiddle with wording and figures to make everything fit again.
Fiddle with figure placement, caption size, prune communication experiment.

\subfloat[Stencil pattern.\label{fig:metg-compute-stencil}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_stencil.pdf}
}
\subfloat[Nearest pattern, 5 dependencies per task.\label{fig:metg-compute-nearest}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_nearest.pdf}
}

\subfloat[Spread pattern, 5 dependencies per task.\label{fig:metg-compute-spread}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_spread.pdf}
}
\subfloat[Nearest pattern, 5 dependencies per task, 4 task graphs.\label{fig:metg-compute-4x-nearest}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_ngraphs_4_nearest.pdf}
}

\caption{METG vs node count for different dependence patterns. Lower is better.\label{fig:metg-compute}}
\end{figure*}

>>>>

\subfloat[Stencil pattern.\label{fig:metg-compute-stencil}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_stencil.pdf}
}
\subfloat[Nearest pattern, 5 deps/task.\label{fig:metg-compute-nearest}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_nearest.pdf}
}

\subfloat[Spread pattern, 5 deps/task.\label{fig:metg-compute-spread}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_spread.pdf}
}
\subfloat[Nearest pattern, 5 deps/task, 4 graphs.\label{fig:metg-compute-4x-nearest}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/compute/metg_ngraphs_4_nearest.pdf}
}

\vspace{-0.15cm}
\caption{METG vs node count for different dependence patterns. Lower is better.\label{fig:metg-compute}}
%% \vspace{-0.05cm}
\end{figure*}

### 2020-03-23 e6_communication.tex
Fiddle with figure placement, caption size, prune communication experiment.

\subfloat[16 bytes per task dependency.\label{fig:efficiency-communication-16}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_16.pdf}
}
\subfloat[256 bytes per task dependency.\label{fig:efficiency-communication-256}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_256.pdf}
}

\subfloat[4096 bytes per task dependency.\label{fig:efficiency-communication-4096}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_4096.pdf}
}
\subfloat[65536 bytes per task dependency.\label{fig:efficiency-communication-65536}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_65536.pdf}
}

\vspace{-0.25cm}
\caption{Efficiency vs task granularity for varying communication (spread pattern, 5 dependencies per task, 4 task graphs, 64 nodes). Higher is better.\label{fig:efficiency-communication}}
\vspace{-0.05cm}
\end{figure*}

>>>>

\subfloat[16 bytes per task dependency.\label{fig:efficiency-communication-16}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_16.pdf}
}
%% \subfloat[256 bytes per task dependency.\label{fig:efficiency-communication-256}]{
%% \includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_256.pdf}
%% }
%%
%% \subfloat[4096 bytes per task dependency.\label{fig:efficiency-communication-4096}]{
%% \includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_4096.pdf}
%% }
\subfloat[65536 bytes per task dependency.\label{fig:efficiency-communication-65536}]{
\includegraphics[width=\columnwidth]{figs/task-bench-results/communication/efficiency_nodes_64_comm_65536.pdf}
}

\vspace{-0.15cm}
\caption{Efficiency vs task granularity for varying communication (spread, 5 deps/task, 4 graphs, 64 nodes). Higher is better.\label{fig:efficiency-communication}}
\vspace{-0.05cm}
\end{figure*}
